Favourable Conservation Status (FCS): <br> Analysis of Bauer et al. (unpublished) Field experiment

### 2022-11-11 R/model_fcs_markdown.Rmd
Update model_fcs_markdown.Rmd

```{r}
dotchart((sites$n), groups = factor(sites$exposition),
         main = "Cleveland dotplot")
sites %>% group_by(exposition) %>% count(site)
boxplot(sites$n)
plot(table((sites$n)), type = "h",
     xlab = "Observed values", ylab = "Frequency")
ggplot(sites, aes(x = n)) + geom_density()
ggplot(sites, aes(sqrt(n))) + geom_density()
```

@@

```{r}
### Posssible priors ###
get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
            seed_density + substrate_depth +
            (1 | site/plot) + (1 | botanist_year),
          data = sites)
### Example of normal distribution
ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
  stat_function(fun = dnorm, n = 101, args = list(mean = 0.1, sd = 1))
### Example of cauchy distribution
ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
  stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1))
### Example of a student t distribution
ggplot(data.frame(x = c(-2, 2)), aes(x = x)) +
  stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5))
```

#### Calculation

@@

```{r}
load(file = here("data", "processed", "model_fcs_1.Rdata"))
m1
load(file = here("data", "processed", "model_fcs_2.Rdata"))
m2
```

@@

```{r}
m_1 <- m1
m_2 <- m3
bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
         re_formula = 1 ~ 1)
bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
         re_formula = 1 ~ 1)
```

@@

```{r}
ppc_dens_overlay(y, yrep1[1:50, ])
ppc_dens_overlay(y, yrep2[1:50, ])
ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$site)
ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$site)
ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$exposition)
ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$exposition)
ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$survey_year_fct)
ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$survey_year_fct)
ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$target_type)
ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$target_type)
ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$seed_density)
ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$seed_density)
ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$sand_ratio)
ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$sand_ratio)
ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$substrate_depth)
ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$substrate_depth)
```

@@

```{r}
ppc_stat(y, yrep1, binwidth = 0.001)
ppc_stat(y, yrep2, binwidth = 0.001)
ppc_stat_grouped(y, yrep1, group = sites$site, binwidth = 0.001)
ppc_stat_grouped(y, yrep2, group = sites$site, binwidth = 0.001)
ppc_stat_grouped(y, yrep1, group = sites$exposition, binwidth = 0.001)
ppc_stat_grouped(y, yrep2, group = sites$exposition, binwidth = 0.001)
ppc_stat_grouped(y, yrep1, group = sites$survey_year_fct, binwidth = 0.001)
ppc_stat_grouped(y, yrep2, group = sites$survey_year_fct, binwidth = 0.001)
ppc_stat_grouped(y, yrep1, group = sites$target_type, binwidth = 0.001)
ppc_stat_grouped(y, yrep2, group = sites$target_type, binwidth = 0.001)
ppc_stat_grouped(y, yrep1, group = sites$seed_density, binwidth = 0.001)
ppc_stat_grouped(y, yrep2, group = sites$seed_density, binwidth = 0.001)
ppc_stat_grouped(y, yrep1, group = sites$sand_ratio, binwidth = 0.001)
ppc_stat_grouped(y, yrep2, group = sites$sand_ratio, binwidth = 0.001)
ppc_stat_grouped(y, yrep1, group = sites$substrate_depth, binwidth = 0.001)
ppc_stat_grouped(y, yrep2, group = sites$substrate_depth, binwidth = 0.001)
```

@@

```{r}
ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object))
ppc_loo_pit_overlay(y, yrep2, lw = weights(loo2$psis_object))
plot(loo1)
plot(loo2)
```

>>>>

```{r}
sites %>% group_by(exposition) %>% count(site)
boxplot(sites$n)
ggplot(sites, aes(x = exposition, y = n)) + geom_quasirandom()
ggplot(sites, aes(x = n)) + geom_histogram(binwidth = 0.03)
ggplot(sites, aes(x = n)) + geom_density()
```

@@

@@

```{r}
load(file = here("data", "processed", "model_fcs_1.Rdata"))
load(file = here("data", "processed", "model_fcs_2.Rdata"))
load(file = here("data", "processed", "model_fcs_3.Rdata"))
```

@@

```{r}
m_1 <- m1
m_2 <- m3
m_1$formula
m_2$formula
```

Conditional and marginal R² values

```{r}
bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
         re_formula = 1 ~ 1)
bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
         re_formula = 1 ~ 1)
```

@@

```{r}
p1 <- ppc_dens_overlay(y, yrep1[1:50, ])
p2 <- ppc_dens_overlay(y, yrep2[1:50, ])
p1 / p2
ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$site)
ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$site)
p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$exposition)
p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$exposition)
p1 / p2
ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$survey_year_fct)
ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$survey_year_fct)
p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$target_type)
p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$target_type)
p1 / p2
p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$seed_density)
p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$seed_density)
p1 / p2
p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$sand_ratio)
p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$sand_ratio)
p1 / p2
p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$substrate_depth)
p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$substrate_depth)
p1 / p2
```

@@

```{r}
p1 <- ppc_stat(y, yrep1, binwidth = 0.001)
p2 <- ppc_stat(y, yrep2, binwidth = 0.001)
p1 / p2
ppc_stat_grouped(y, yrep1, group = sites$site, binwidth = 0.001)
ppc_stat_grouped(y, yrep2, group = sites$site, binwidth = 0.001)
p1 <- ppc_stat_grouped(y, yrep1, group = sites$exposition, binwidth = 0.001)
p2 <- ppc_stat_grouped(y, yrep2, group = sites$exposition, binwidth = 0.001)
p1 / p2
ppc_stat_grouped(y, yrep1, group = sites$survey_year_fct, binwidth = 0.001)
ppc_stat_grouped(y, yrep2, group = sites$survey_year_fct, binwidth = 0.001)
p1 <- ppc_stat_grouped(y, yrep1, group = sites$target_type, binwidth = 0.001)
p2 <- ppc_stat_grouped(y, yrep2, group = sites$target_type, binwidth = 0.001)
p1 / p2
p1 <- ppc_stat_grouped(y, yrep1, group = sites$seed_density, binwidth = 0.001)
p2 <- ppc_stat_grouped(y, yrep2, group = sites$seed_density, binwidth = 0.001)
p1 / p2
p1 <- ppc_stat_grouped(y, yrep1, group = sites$sand_ratio, binwidth = 0.001)
p2 <- ppc_stat_grouped(y, yrep2, group = sites$sand_ratio, binwidth = 0.001)
p1 / p2
p1 <- ppc_stat_grouped(y, yrep1, group = sites$substrate_depth, binwidth = 0.001)
p2 <- ppc_stat_grouped(y, yrep2, group = sites$substrate_depth, binwidth = 0.001)
p1 / p2
```

@@

```{r}
p1 <- ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object))
p2 <- ppc_loo_pit_overlay(y, yrep2, lw = weights(loo2$psis_object))
p1 / p2
plot(loo1)
plot(loo2)
```
